Supplementary material: The increasing cost of happiness

### 2021-02-08 src/supplementary.Rmd
Major commit: Added counterfactual, added years 2002:2018 to main, updated format for PNAS

```{r setup, include=FALSE}
library(tidyverse)
library(flextable)
library(bayesplot)
library(patchwork)

@@

#### Model Selection (2002-2018)

##### Figure S1. Linear model evidence (WAIC~linear~ — WAIC~piecewise~)
```{r complete_waic}
waic_result <- read_rds("../results/model_comparisons_waic_R2_losat.RDS")

waic_result %>%
  select(model, year, elpd_diff, se_diff) %>%
  filter(elpd_diff != 0) %>%
  rowwise() %>%
  mutate(samples = list(rnorm(n = 1e5, 
                              mean = elpd_diff * -2, # for linear advantage
                              sd   = se_diff *  2)),
         year = paste0("AD", year)
         ) %>%
  select(year, samples) %>%
  group_by(year) %>%
  unnest(samples) %>% 
  mutate(sample_id = c(1:1e5)) %>%
  pivot_wider(id_col = "sample_id", names_from = "year", values_from = "samples") %>%
  select(-sample_id) -> d1

# "fix" d1
colnames(d1) <- rev(colnames(d1))

@@

p2 <- mcmc_intervals(x = d1,
  pars = colnames(d1),
  prob = 0.0,
  prob_outer = .95
  ) +
  scale_x_continuous(
    limits = c(-200, 150)
    ) +
  geom_vline(aes(xintercept = 0), color = "grey90") +
  theme_test() +
  labs(
    subtitle = "Satisfaction",
    x = "WAIC difference (95% interval)")

waic_result <- read_rds("../results/model_comparisons_waic_R2_gh9.RDS")

waic_result %>%
  select(model, year, elpd_diff, se_diff) %>%
  filter(elpd_diff != 0) %>%
  rowwise() %>%
  mutate(samples = list(rnorm(n = 1e5, 
                              mean = elpd_diff * 2, # for pw advantage
                              sd   = se_diff *  2)),
         year = paste0("AD", year)
         ) %>%
  select(year, samples) %>%
  group_by(year) %>%
  unnest(samples) %>% 
  mutate(sample_id = c(1:1e5)) %>%
  pivot_wider(id_col = "sample_id", names_from = "year", values_from = "samples") %>%
  select(-sample_id) -> d2

p1 <- mcmc_intervals(x = d2,
           pars = rev(colnames(d2)),
           prob = 0.00,
           prob_outer = 0.95
           ) +
  scale_x_continuous(
    limits = c(-200, 150)
    ) +
  geom_vline(aes(xintercept = 0), color = "grey90") +
  theme_test() +
  labs(
    subtitle = "Happiness")
```

```{r Figure_S1, fig.width=6.5, fig.height=7, dpi=300}
p1 / p2
```

```
Figure S1 legend: Differences in posterior evidence (WAIC) for a linear fit over a piecewise fit for satisfaction (blue) and happiness (red). The filled circle indicates the mean of the distribution and the horizontal bars represents the 95% credible interval. A difference greater than zero is support for the linear model and a difference below zero is support for the piecewise model.
```

@@

#### Parameter Estimation (2002-2018)

##### Figure S2. Posterior distributions of &omega; (95% distribution)  
```{r gh9_omega}
path_to_gh9_fits <- list.files(
  path = "../results",
  pattern = '^fit_cp_hifdip_gh9_cov_.*.RDS$',
  full.names = TRUE
)

posterior_alphas <- list()
for (pathtofile in path_to_gh9_fits) {
  df <- read_rds(pathtofile) %>%
    as.data.frame() %>%
    select(b_alpha_Intercept)

  colnames(df) <- paste0("param_", substring(pathtofile, 34, 37))

  posterior_alphas <- bind_cols(posterior_alphas, df)
}

posterior_alphas %>%
  mutate_all(.funs = ~brms::inv_logit_scaled(., 0, 100)*10) -> posterior_omegas

posteriors_trim <- posterior_omegas %>%
  mutate(
    # param_2010 = (param_2010 + param_2011)/2,
    param_2003 = (param_2002 + param_2004)/2)

p3 <- mcmc_intervals(
  posteriors_trim,
  pars = rev(colnames(posteriors_trim)),
  prob = 0.0, 
  prob_outer = .95 
  ) +
  geom_vline(aes(xintercept = median(posteriors_trim$param_2002)), 
             color = "gray", 
             linetype = 3) +
  theme_test() +
  coord_cartesian(xlim = c(20, 200)) +
  labs(
    subtitle = "Happiness",
    x = "")
```

```{r losat_omega}
path_to_losat_fits <- list.files(
  path = "../results",
  pattern = '^fit_cp_hifdip_losat_cov_.*.RDS$',
  full.names = TRUE
)

posterior_alphas <- list()
for (pathtofile in path_to_losat_fits) {
  df <- read_rds(pathtofile) %>%
    as.data.frame() %>%
    select(b_alpha_Intercept)

  colnames(df) <- paste0("param_", substring(pathtofile, 36, 39))

  posterior_alphas <- bind_cols(posterior_alphas, df)
}

posterior_alphas %>%
  mutate_all(.funs = ~brms::inv_logit_scaled(., 0, 100)*10) -> posterior_omegas

posteriors_trim <- posterior_omegas %>%
  mutate(
    param_2006 = (param_2007 + param_2005)/2)

p4 <- mcmc_intervals(
  posteriors_trim,
  pars = rev(colnames(posteriors_trim)),
  prob = 0.0, 
  prob_outer = .95 
  ) +
  geom_vline(aes(xintercept = median(posteriors_trim$param_2002)), 
             color = "gray", 
             linetype = 3) +
  theme_test() +
  coord_cartesian(xlim = c(20, 200)) +
  labs(
    subtitle = "Satisfaction",
    x = "Household income ($000s)")
```

```{r Figure_S2, fig.width = 6, fig.height = 7, dpi=300}
p3 / p4
```

```
Figure S2 legend: Posterior distribution of the change point parameter representing the location in household income ($) for each year. Horizontal bar represents the 95% credible interval.
```

@@

#### Change point model parameter estimates

@@

The Bayes R^2^ = 0.03964581 ±0.001497172 (0.03672371-0.04262236)

@@

@@

population_summary %>%
  mutate(Parameter = str_remove(Parameter, "_Intercept")) %>%
  arrange(Parameter, desc(Year)) %>%
  flextable() %>%
  merge_v(j = 1) %>%
  valign(j = 1, valign = "top") %>%
  bg(i = ~Parameter %in% c("b0", 
                           "b2", 
                           "b4", 
                           "b6"), 
     bg = "grey90", 
     part = "body") %>%
  bg(i = ~Parameter %in% c("sigma"), 
     bg = "#b3cde0", 
     part = "body") %>%
  colformat_num(j = 3:6, digits= 3) %>%
  colformat_num(j = 7, digits= 1) %>%
  set_caption("Table S1. Population-level piecewise parameter estimates for happiness") %>%
  autofit()
```

@@

population_summary %>%
  mutate(Parameter = fct_relevel(Parameter, "Intercept", "dollars", "grad")) %>%
  arrange(Parameter, desc(Year)) %>%
  flextable() %>%
  merge_v(j = 1) %>%
  valign(j = 1, valign = "top") %>%
  bg(i = ~Parameter %in% c("dollars",
                           "age",
                           "male"),
     bg = "grey90",
     part = "body") %>%
  bg(i = ~Parameter %in% c("sigma"), 
     bg = "#b3cde0", 
     part = "body") %>%
  colformat_num(j = 3:6, digits= 3) %>%
  colformat_num(j = 7, digits= 1) %>%
  set_caption("Table S2. Population-level linear parameter estimates for happiness") %>%
  autofit()
```

@@

```{r losat_pw_summary, ft.align="left"}
population_summary <- tibble()
for (pathtofile in path_to_losat_fits) {
  fit_summary <- read_rds(pathtofile) %>%
    summary()

@@

population_summary %>%
  mutate(Parameter = str_remove(Parameter, "_Intercept")) %>%
  arrange(Parameter, desc(Year)) %>%
  flextable() %>%
  merge_v(j = 1) %>%
  valign(j = 1, valign = "top") %>%
  bg(i = ~Parameter %in% c("b0", 
                           "b2", 
                           "b4", 
                           "b6"), 
     bg = "grey90", 
     part = "body") %>%
  bg(i = ~Parameter %in% c("sigma"), 
     bg = "#b3cde0", 
     part = "body") %>%
  colformat_num(j = 3:6, digits= 3) %>%
  colformat_num(j = 7, digits= 1) %>%
  set_caption("Table S3. Population-level piecewise parameter estimates for satisfaction") %>%
  autofit()
```

@@

population_summary %>%
  mutate(Parameter = fct_relevel(Parameter, "Intercept", "dollars", "grad")) %>%
  arrange(Parameter, desc(Year)) %>%
  flextable() %>%
  merge_v(j = 1) %>%
  valign(j = 1, valign = "top") %>%
  bg(i = ~Parameter %in% c("dollars",
                           "age",
                           "male"),
     bg = "grey90",
     part = "body") %>%
  bg(i = ~Parameter %in% c("sigma"), 
     bg = "#b3cde0", 
     part = "body") %>%
  colformat_num(j = 3:6, digits= 3) %>%
  colformat_num(j = 7, digits= 1) %>%
  set_caption("Table S4. Population-level linear parameter estimates for happiness") %>%
  autofit()
```

@@

Examination of the residual plots from the piecewise models of happiness confirms the residuals were evenly distributed around zero and there was little indication of heterscedascity. There was little evidence that the piecewise models of happiness were not appropriate for the data.

#### Non-linear fits

@@

##### Figure S4. Cubic spline of household wealth on satisfaction and happiness
```{r losat_gh9_hwnwip}
source("../src/happyfun.r")
happywealth <- read_rds("../data/happywealth.rds")

p1 <- happywealth %>%
  filter(hifdip_adj > 0) %>%
  rename(Satisfaction = losat, `Household wealth` = hifdip_adj) %>% 
  plot_inflection_cubic(Satisfaction, `Household wealth`) +
  scale_x_continuous(trans = "log", 
                     breaks = c(5, 10, 20, 40, 80, 160),
                     limits = c(2.5, 170))

p2 <- happywealth %>%
  filter(hifdip_adj > 0) %>%
  rename(Happiness = gh9, `Household wealth` = hifdip_adj) %>% 
  plot_inflection_cubic(Happiness, `Household wealth`) +
  scale_x_continuous(trans = "log", 
                     breaks = c(5, 10, 20, 40, 80, 160),
                     limits = c(2.5, 170))
```
```{r cubic_plot, fig.height=9, fig.width=11}
p1 / p2
```

@@

##### Figure S5. Prior predictive plot
(Not included)

@@

##### Figure S6. Marginal effect of wealth on satisfaction by year (95% CI)  
(Not included)
```{r figure_s6_df, eval=F}
# Do not run

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(flextable)
library(gtsummary)
library(bayesplot)
library(patchwork)

@@

#### Sample characteristics

The broad demographic characteristics of the sample at each fourth year wave are presented below in Table S1.

```{r table_1, ft.align="left"}
happywealth <- read_rds("../data/happywealth.rds")

happywealth %>%
  filter(year %in% c(2002, 2006, 2010, 2014, 2018)) %>%
  filter(!student, !top_hifdip, (!is.na(losat)|!is.na(gh9))) %>%
  mutate(
    Sex = if_else(male, "Male", "Female"),
    Education = fct_collapse(
      edu,
      `High school or less` = c("None", "In school", "Highschool"),
      Graduate = c("Grad")
      ),
    Workforce = case_when(
      workforce & !unemployed ~ "Employed",
      unemployed ~ "Unemployed",
      TRUE ~ "Not in labour force"
      ),
    `Relationship status` = case_when(
      single ~ "Single",
      coupled ~ "Married",
      TRUE ~ "Divorced/Widow"
      ),
    Workforce = fct_relevel(Workforce, "Employed", "Unemployed"),
    `Relationship status` = fct_relevel(`Relationship status`, "Single", "Married")
    ) %>%
  select(
    year, 
    `Life satisfaction` = losat, `Happiness` = gh9,
    Sex, `Age (years)` = age, Education, Workforce, `Relationship status`, 
    `Chronic illness` = chronic, SEIFA, `Household size` = hhsize,
  ) %>% 
  tbl_summary(
    by = year,
    missing = "no",
    statistic = 
      list(all_continuous() ~ "{mean} (±{sd})",
           all_categorical() ~ "{n} ({p}%)"),
    digits = all_continuous() ~ 1,
    missing_text = "(Missing)" 
    ) %>%
  modify_header(stat_by = "{level}\nN = {style_number(n)}") %>%
  as_flex_table() %>%
  set_caption(caption = "Table S1. Demographic characteristics of the sample") %>%
  align(part = "body") %>%
  valign(valign = "top", part = "header") %>%
  fontsize(size = 9.5, part = "all") %>%
  width(j = 1, width = 1.5) %>%
  width(j = 2:6, width = 1)
```

Average life satisfaction levels were very steady between 2002-2018, while average happiness score decreased slightly over the 17 years. The proportions of each sex and relationship status were stable over time, as were the average household size and SEIFA index. However age and chronic health conditions tended to increase over time, indicating a slight increase in the age of the panel over time (1.8 years) but not that of a cohort study which would be 16 years. Education levels (i.e., graduate percentage) also tended to increase over time, while changes in the workforce varied with economic circumstances.

#### Model Selection

We compared the posterior evidence of a linear- over a nonlinear- relationship between each wellbeing variable and income (i.e., WAIC~linear~ — WAIC~piecewise~). Thus a WAIC difference greater than zero indicated evidence for a linear relationship. A WAIC difference less than zero indicated evidence for a nonlinear (piecewise) relationship.

##### Figure S1. Linear model evidence (WAIC~linear~ — WAIC~piecewise~)

```{r complete_waic}
waic_gh9 <- read_rds("../results/model_comparisons_waic_R2_gh9.RDS")

waic_gh9 %>%
  select(model, year, elpd_diff, se_diff) %>%
  filter(elpd_diff != 0) %>%
  rowwise() %>%
  mutate(samples = list(rnorm(n = 1e5, 
                              mean = elpd_diff * 2, # for pw advantage
                              sd   = se_diff *  2)),
         year = paste0("AD", year)
         ) %>%
  select(year, samples) %>%
  group_by(year) %>%
  unnest(samples) %>% 
  mutate(sample_id = c(1:1e5)) %>%
  pivot_wider(id_col = "sample_id", names_from = "year", values_from = "samples") %>%
  select(-sample_id) -> d2

p1 <- mcmc_intervals(x = d2,
           pars = colnames(d2),
           prob = 0.00,
           prob_outer = 0.95
           ) +
  scale_x_continuous(
    limits = c(-200, 150)
    ) +
  scale_y_discrete(labels = as.character(2002:2018)) +
  geom_vline(aes(xintercept = 0), color = "grey90") +
  theme_test() +
  labs(
    subtitle = "Happiness")

waic_losat <- read_rds("../results/model_comparisons_waic_R2_losat.RDS")

waic_losat %>%
  select(model, year, elpd_diff, se_diff) %>%
  filter(elpd_diff != 0, year > 2001) %>%
  rowwise() %>%
  mutate(samples = list(rnorm(n = 1e5, 
                              mean = elpd_diff * -2, # for linear advantage
                              sd   = se_diff *  2)),
         year = paste0("AD", year)
         ) %>%
  select(year, samples) %>%
  group_by(year) %>%
  unnest(samples) %>% 
  mutate(sample_id = c(1:1e5)) %>%
  pivot_wider(id_col = "sample_id", names_from = "year", values_from = "samples") %>%
  select(-sample_id) -> d1

@@

p2 <- mcmc_intervals(x = d1,
  pars = rev(colnames(d1)),
  prob = 0.0,
  prob_outer = .95
  ) +
  scale_x_continuous(
    limits = c(-200, 150)
    ) +
  scale_y_discrete(labels = as.character(2002:2018)) +
  geom_vline(aes(xintercept = 0), color = "grey90") +
  theme_test() +
  labs(
    subtitle = "Satisfaction",
    x = "WAIC difference (95% CI)")
```

```{r figure_s1, fig.width=6.5, fig.height=7, dpi=300}
p1 / p2
```

```
Figure S1 legend: Differences in posterior evidence for a linear fit over a piecewise fit (WAIC) for happiness (red) and satisfaction (blue). The filled circle indicates the mean of the distribution and the horizontal bars represents the 95% credible interval. A difference greater than zero is support for the linear model and a difference below zero is support for the piecewise model.
```

The posterior evidence from model selection revealed the nonlinear (piecewise) fit of _happiness_, but not _satisfaction_, was credibly superior to a linear fit in each year. Figure S1 shows the 95% credible interval of the difference in WAIC values for the linear over nonlinear fits for happiness was below zero with no overlap for each year, indicating consistent support for the nonlinear model. By contrast, the WAIC differences for the satisfaction models were generally positive, indicating the superiority of the linear fit for this dependent variable. Overall the posterior evidence suggests that happiness and satisfaction have distinct relationships with household income; satisfaction tends to increase linearly with income, while a change point exists in the relationship between happiness and household income.

@@

#### Model predictions (2002-2018)

The posterior estimates of the piecewise model indicated that the relationship between happiness and income changed over time between 2002 and 2018. One implication of such a change is the disparity in happiness between income groups has increased. This will occur as more people fall below the change point over time and so are subject to the steep region of the function where income and happiness are strongly related. To directly examine the implications of our model for such inequities in happiness, we used the model to estimate or _predict_ the happiness of two different income levels: one income level which fell below the change points between 2002-2018 (\$40K/yr); and another level which always remained above the change points over the same period (\$75K/yr). Figure S2 below presents the happiness levels (in SD units/year) for each income level as well as the difference in happiness between them (∆).

@@

##### Figure S2. Happiness (SD units) at $40K/yr and $75K/yr from 2002-2018 
```{r figure_s2, fig.width=7, fig.height=5, dpi=300, eval=T}
path_to_gh9_fits <- list.files(
  path = "../results/incl_topcodes/with_pweights/",
  pattern = "^fit_nl_hifdip_gh9_4cov_pwt_.*.RDS$",
  full.names = TRUE
)

predicted_fits <- list()
for (pathtofile in path_to_gh9_fits) {
  fit <- read_rds(pathtofile)

  ans <- model.frame(fit) %>%
    summarise_all(median)

  newdat = data.frame(
    dollars = c(4, ans[, "dollars"], 7.5),
    age = rep(ans[, "age"], 3),
    age_sq = rep(ans[, "age_sq"], 3),
    male = as.logical(rep(ans[, "male"], 3)), 
    grad = as.logical(rep(ans[, "grad"], 3)),
    pweights = rep(ans[, "pweights"], 3)
  )

  df <- fitted(fit, newdata = newdat) %>% 
    as_tibble() %>%
    mutate(
      Dollars = c("$40K", "\u03bc", "$75K"),
      year = as.numeric(
        substring(pathtofile, nchar(pathtofile)-7, nchar(pathtofile)-4)
        )
      )

  predicted_fits <- bind_rows(predicted_fits, df)
}

predicted_fits %>%
  select(Estimate, Dollars, year) %>%
  filter(Dollars %in% c("$75K", "$40K")) %>%
  spread(Dollars, Estimate) %>%
  mutate(`$75K - $40K (∆)` = `$75K` - `$40K`) %>%
  gather(income, happiness, -year) %>%
  mutate(income = fct_relevel(income, "$40K", "$75K")) %>%
  ggplot(aes(x = year, y = happiness, color = income)) +
  geom_point(size = 4, alpha = 0.25) +
  geom_smooth(method = "loess", se = F, span = 3) +
  facet_wrap(~income) +
  labs(caption = "Source:     HILDA, University of Melbourne
                 Predicted happiness scores (SD unit) from piecewise regression on real household income", 
       x = "", y = "") -> p

source("ft_themes.r")

p +
  ft_theme() +
  ggthemes::scale_colour_wsj() +
  theme(legend.position = "none",
        plot.title = element_text(size = 19),
        strip.text = element_text(size = 12))
```

```{r alt_figure_s2, fig.width=7, fig.height=5, dpi = 300, eval=F}
happywealth %>%
  filter(!student) %>%
  filter(!top_hifdip) %>%
  select(year, xwaveid, gh9, income = hh_disp_inc_eq, weights) %>%
  filter(year %in% 2002:2018) %>%
  mutate(
    year = paste0("param_", year),
    income = income/1000) %>%
  mutate(
    year = extract_numeric(year),
    income_group = case_when(
      income > 35 & income < 45 ~ "$40K",
      income > 70 & income < 80 ~ "$75K"
    )) %>%
  group_by(year) %>%
  mutate(
    happiness = as.vector(scale(gh9)),
    ) %>%
  filter(!is.na(income_group)) %>%
  group_by(year, income_group) %>%
  summarise(
    Happiness = mean(happiness, na.rm = T)
    ) %>% 
  ungroup() %>%
  spread(income_group, Happiness) %>%
  mutate(`$75K - $40K (∆)` = `$75K` - `$40K`) %>%
  gather(key, val, `$40K`:`$75K - $40K (∆)`) %>%
  mutate(key = fct_relevel(key, c("$40K", "$75K"))) %>%
  ggplot(aes(x = year, y = val, color = key)) +
    geom_point(size = 4, alpha = 0.25) +
    geom_smooth(span = 3, se = F) +
    facet_wrap(~key) +
    labs(caption = "Source:     HILDA, University of Melbourne
                 Observed happiness scores (SD unit)", 
     x = "", y = "") -> p

p +
  ft_theme() +
  ggthemes::scale_colour_wsj() +
  theme(legend.position = "none",
        plot.title = element_text(size = 19),
        strip.text = element_text(size = 12))
```
```
Figure S2 legend: The difference (∆) in happiness between a household income of $40K per year and a household income of $75K per year has increased between 2002 and 2018.
```

Figure S2 shows the disparity in happiness between two fixed income levels, \$40K/year (below the change points) and \$75K/year (above the change points). In 2002, a household income of \$40K/year achieved a near average level of happiness relative to everyone else that year, however by 2018 happiness had declined to lower than average levels relative to the population. By contrast, a household income of \$75K/year enjoyed a higher than average level of happiness for the entire period. The difference (∆) in happiness between these two income levels doubled over the period. The increasing disparity in happiness between the rich and the poor implies that happiness has became more inequitable over the period.

Examination of the residual plots from the piecewise models of happiness confirms the residuals were evenly distributed around zero and there was little indication of heterscedascity. Overall, there was little evidence that the piecewise models of happiness were not appropriate for the data.

#### Complete parameter estimates and fit statistics

@@

The Bayes R^2^ = `r round(0.0403964581, 3)` ±`r round(0.001497172, 3)` (95%CI `r round(0.03672371,3)` — `r round(0.04262236, 3)`)

@@

  fixed_summary <- fit_summary$fixed %>%
    as_tibble(rownames = "Parameter") %>%
    bind_rows(sigma_summary) %>%
    mutate(
      Year = substring(pathtofile, nchar(pathtofile)-7, nchar(pathtofile)-4)
      ) %>%
    select(Parameter, Year, everything())

@@

population_summary %>%
  mutate(Parameter = str_remove(Parameter, "_Intercept")) %>%
  arrange(Parameter, desc(Year)) %>%
  filter(Year > 2001) %>%
  flextable() %>%
  merge_v(j = 1) %>%
  valign(j = 1, valign = "top") %>%
  bg(i = ~Parameter %in% c("b0", 
                           "b2", 
                           "b4", 
                           "b6"), 
     bg = "grey90", 
     part = "body") %>%
  bg(i = ~Parameter %in% c("sigma"), 
     bg = "#b3cde0", 
     part = "body") %>%
  colformat_num(j = 3:6, digits= 3) %>%
  colformat_num(j = 7, digits= 1) %>%
  set_caption("Table S1. Piecewise parameter estimates for happiness") %>%
  autofit()
```

@@

population_summary %>%
  mutate(Parameter = fct_relevel(Parameter, "Intercept", "dollars", "grad")) %>%
  arrange(Parameter, desc(Year)) %>%
  flextable() %>%
  merge_v(j = 1) %>%
  valign(j = 1, valign = "top") %>%
  bg(i = ~Parameter %in% c("dollars",
                           "age",
                           "male"),
     bg = "grey90",
     part = "body") %>%
  bg(i = ~Parameter %in% c("sigma"), 
     bg = "#b3cde0", 
     part = "body") %>%
  colformat_num(j = 3:6, digits= 3) %>%
  colformat_num(j = 7, digits= 1) %>%
  set_caption("Table S2. Linear parameter estimates for happiness") %>%
  autofit()
```

@@

```{r losat_pw_summary, ft.align="left"}
path_to_losat_fits <- list.files(
  path = "../results",
  pattern = '^fit_cp_hifdip_losat_cov_.*.RDS$',
  full.names = TRUE
)

population_summary <- tibble()
for (pathtofile in path_to_losat_fits) {
  fit_summary <- read_rds(pathtofile) %>%
    summary()

@@

population_summary %>%
  mutate(Parameter = str_remove(Parameter, "_Intercept")) %>%
  arrange(Parameter, desc(Year)) %>%
  flextable() %>%
  merge_v(j = 1) %>%
  valign(j = 1, valign = "top") %>%
  bg(i = ~Parameter %in% c("b0", 
                           "b2", 
                           "b4", 
                           "b6"), 
     bg = "grey90", 
     part = "body") %>%
  bg(i = ~Parameter %in% c("sigma"), 
     bg = "#b3cde0", 
     part = "body") %>%
  colformat_num(j = 3:6, digits= 3) %>%
  colformat_num(j = 7, digits= 1) %>%
  set_caption("Table S3. Piecewise parameter estimates for satisfaction") %>%
  autofit()
```

@@

population_summary %>%
  mutate(Parameter = fct_relevel(Parameter, "Intercept", "dollars", "grad")) %>%
  arrange(Parameter, desc(Year)) %>%
  flextable() %>%
  merge_v(j = 1) %>%
  valign(j = 1, valign = "top") %>%
  bg(i = ~Parameter %in% c("dollars",
                           "age",
                           "male"),
     bg = "grey90",
     part = "body") %>%
  bg(i = ~Parameter %in% c("sigma"), 
     bg = "#b3cde0", 
     part = "body") %>%
  colformat_num(j = 3:6, digits= 3) %>%
  colformat_num(j = 7, digits= 1) %>%
  set_caption("Table S4. Linear parameter estimates for happiness") %>%
  autofit()
```

@@

#### Additional non-linear fits

@@

##### Figure S5. Cubic spline of household wealth on satisfaction and happiness
```{r cubic_plot, fig.height=9, fig.width=11}
source("../src/happyfun.r")
happywealth <- read_rds("../data/happywealth.rds")

p1 <- happywealth %>%
  filter(!student, !top_hifdip) %>%
  rename(Satisfaction = losat, `Household income` = hh_disp_inc_eq) %>% 
  plot_inflection_cubic(Satisfaction, `Household income`) +
  scale_x_continuous(
    # trans = "log", 
    # breaks = c(5, 10, 20, 40, 80, 160),
    limits = c(5, 170))

p2 <- happywealth %>%
  filter(!student, !top_hifdip) %>%
  rename(Happiness = gh9, `Household income` = hh_disp_inc_eq) %>% 
  plot_inflection_cubic(Happiness, `Household income`) +
  scale_x_continuous(
    # trans = "log", 
    # breaks = c(5, 10, 20, 40, 80, 160),
    limits = c(5, 170))

p1 / p2
```

@@

##### Figure S6. Prior predictive plot
(Not included)

@@

##### Figure S7. Marginal effect of wealth on satisfaction by year (95% CI)  
(Not included)
```{r figure_s6_df, eval=F}
# Do not run
